\chapter{Acknowledgements}
I'd like to thank my friends in the lab, some of whom were responsible for convincing me to take on this daunting project! Craig Burden, Gareth Callanan, Roberto Aldera, Munnawar Tayob, Michael Evans and Brad Stocks. 

All the post graduate researchers in the lab (from fourth year number... 3?) -- thank you for the endless support and missions to the UCT pub! I'd specifically like to thank Callen Fisher for the assistance, sharp mind, and sometimes harsh words to set us on track without hesitation! 

To the mechatronics lab squash team -- I hope to be able to play against you all again, I restrung my racquet just for that chance... Callen (still to beat), Stacey, Neil, Arnold, Givs, Tinashe (most improved and serious comeback!), Robyn.

Ben Bingham and Luke Bell -- your contribution to the project was a great kick-start that helped avoid a lot of trouble! Thank you for being quick to help.

Brendan Daniels and Justin Pead -- you were there day in and out, dealing with that pesky laser cutter, providing handfuls of components, defusing near blown LiPos, and providing your time to 3D print parts for Baleka.

My family -- for all the tea ferried up to my room, dealing with my hermit like habits in the final stretch, and the care!

Last and certainly not least, my supervisor, Dr. Amir Patel -- your guidance was strong, and your words and endless enthusiasm gave confidence when needed most! The project was a daunting task and you helped define my research vision.
