\chapter{Workspace Data}

Research data is separated into the folders as listed below, available on CD or by request:

\begin{itemize}
\item background: various literature review documents.
\item baleka-stm32f4-code: embedded system code.
\item BalekaQtApp: Qt GUI code.
\item baleka-system-kicad: start of electronics CAD representation of embedded system.
\item communication: embedded system and motor driver communication protocol work.
\item datasheets: various datasheets of components used in leg design.
\item documentation: start of documentation write-up for Driveware use and configuration.
\item drawio: draw.io graphic design application files used for report.
\item experiments: experimental test data and video data.
\item kinematics: various files with kinematic constraints and motor driver position limits.
\item LATEX: report write-up in LATEX.
\item miscellaneous: mass logs, motor model tuning, and performance tables.
\item solidworks-original: compressed folder of all Ben Bingham's original CAD work.
\item VacWorkLeg-original: compressed folder of all Luke Bell's original work.
\item workspace-atollic: initial development of embedded system code.
\item workspace-driveware: Driveware motor driver configuration files.
\item workspace-inemo: work completed on iNemo code developed by Callen Fisher.
\item workspace-matlab: Matlab scripts and saved workspaces.
\item workspace-openscad: OpenSCAD programmatic CAD models.
\item workspace-solidworks: CAD assemblies, designs and virtual models developed in Solidworks.
\end{itemize}

The final report write-up PDF can be found in the root directory, named report.pdf.